Tools for identifying implausible counts

### 2019-04-04 Rmd/count_check_MS.Rmd
pollen in ms

loadd(bird_singleton_summary)
loadd(testate_counts, testate_summary)
loadd(last_chance_meta)
```

@@

Dataset 3 is a `r #nrow(d3)` pollen stratigraphy extracted from Neotoma. The associated paper (anonymsed here) reports that count sums are at least ###. All counts in dataset 3 sum to ###-###... No singletons.

>>>>

loadd(bird_singleton_summary)
loadd(testate_counts, testate_summary)
loadd(last_chance_meta)
loadd(pollen1_summary)

```

@@

Dataset 3 is a `r n_groups(readd(pollen1_counts))` count pollen stratigraphy extracted from Neotoma. The associated paper (anonymised here) reports that count sums are 200 (excluding fern spores). Unexpectedly, only `r pollen1_summary$count$has_singletons %>% insist(. == 1) %>% as.english()` of the counts has a singleton. The other counts have minimum abundances of two or four pollen grains. With the exception of the single singleton, all `r pollen1_summary$individual$n %>% invisible()` species counts are divisible by two`r pollen1_summary$individual$not_two %>% insist(. == 1) %>% invisible()`. The probablility that these counts reflects the true nature of the pollen assemblages is exceedingly low; it is far more likely that the data have been mishandled in some way.
